\chapter{Proposing the Future}
\begin{epigraphs}
  \qitem{\textquotedblleft The best thing about the future is that it comes one day at a time.\textquotedblright}
        {Abraham Lincoln}
\end{epigraphs}
In software engineering, the agile process outlines how a software isn't created all at once but progresses over its features one by one. Similarly, for this mobile application of ASET ALiAS, there would certainly be new requirements that would need to be met and could be fulfilled with addition of fresh features to this mobile application. Some of the possible features that can be foreseen are:
\begin{enumerate}
\item \textbf{GitHub authorization}: GitHub as discussed in chapter \ref{chap:devTools} is a widely used technology as a version controlled system. The club also gives its speaker and community an opportunity to propose a talk by creating an issue to our logistics repository. With this feature, it would be easier to perform this function and most of our documents would be much more easily accessible. 
\item \textbf{Dedicated chat application}: Currently most of the communication takes place on Telegram, Whatsapp and IRC channel. If someday there arises a need for collaborative unified communication across all platforms, then this feature would be the go to option to implement.
\item \textbf{Twitter and other social media integration}: ASET ALiAS is an active community on social media and is regularly updated regarding its happenings at the university or online. Having these integrated would have all the information in one place.
\end{enumerate}

