\chapter{Results and Discussion}
\label{chap:resultsAndDiscussion}
\begin{epigraphs}
  \qitem {\textquotedblleft The combination of hard work and smart work is efficient work.\textquotedblright}
         {Robert Half}
\end{epigraphs}

Inspired by the use of most widely active social networking sites like Facebook, Instagram and Pinterest, I decided to work on React Native as it is used for developing cross platform native mobile applications.  More than this was the hope to be able to develop applications that look good as they give good consideration of the application's UI (user interface) and UX (user experience). \par \medskip
In the first week I started with understanding the process taken under mobile app development and the trends in technologies being offered currently. I tried out various frameworks available in Java, JavaScript and Python, but found React Native, which is based on JavaScript, to be a good head start.\par \medskip
For week two, I started with React.js and React Web. With these, I created a TODO web app which was further converted to a mobile version using React Native. I also tried on making two more types of app. One used the Open Weather Data available and fetched the current location's data and displayed the current weather. The other one was on scrolling cards which would make the respective markers move in the map. \par \medskip
In week three, I developed different screens per tab at https://asetalias.in/ and then displayed the fetched data of all the events from the site. I took this up as an exercise simultaneously. This initiated my coding process. I also developed a system to fetch timely notifications to the application. \par \bigskip
\newpage
Talking about accomplishments, the targets and accomplishments on a weekly basis has been summarized in table \ref{tab:schedule}.

\begin{center}
  \begin{longtable} {|c|p{5cm}|p{5cm}|}
    \hline\\
    \textbf{Week} & \textbf{Target} & \textbf{Accomplishment}\\
    \hline
    1& Understand the needs of mobile app development and the current trends in the market. Try out various technologies available and find the apparently best fit for the time being.& Read code and documentation on mobile app development with java, kivy in python, django-for-android in python, native and hybrid app development. Chose React Native as my go to technology for this project.\\
    \hline
    2& Work on React.js, React Web and basics of React Native.& Created React Native apps: 
    \begin{enumerate} 
        \item TODO app in React Web and React Native
        \item Current weather of current location is shown using Open Weather Data API
        \item Moving markers on a map on scrolling through their respective cards.
    \end{enumerate}\\
    \hline
    3& Start developing the app for ASET ALiAS.& Made different screens for different tabs needed as a functionality of app. Fetched webinar and events data from https://asetalias.in/. Designed the app using native base components \\
    \hline
    \caption{Weekly log of accomplishments}
  \end{longtable}
  
  \label{tab:schedule}
\end{center}